---
title: "WIP Demo"
author: "Kai Jeffreys"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Initialize Set Up
### Load in the functions
```{r}
source("wip_functions.R")
```


### Load in files
These files could include a DEM, training points, other rast files, or polygon files

```{r}
r <- terra::rast("PackForest/PF_DTM3.tif")
pts <- terra::vect("PackForest/PF_trainingdata.shp")
```

# Create elevation derivatives
We will use the `surface_met` function in order to create the elevation derivatives. In order to get it to run, one needs to input


```{r}
elev1 <- surface_met(r, len = 20, elev_dev = c("grad", "prof", "plan"))
elev2 <- surface_met(r, len = 100, elev_dev = c("grad", "prof", "plan"))
elev3 <- surface_met(r, len = 10, elev_dev = c("twi"))
```

# Build the model



```{r}
mod1 <- build_model(in_rasts = elev1, train = pts)
mod2 <- build_model(in_rasts = c(elev1, elev2, elev3), train = pts)
mod3 <- build_model(in_rasts = c(elev1, elev2, elev3), train = pts,
                    model_type = "glm")
mod4 <- build_model(in_rasts = c(elev1, elev2, elev3), train = pts,
                    model_type = "knn", model_params = list(k = 5))
```

## Get an estimate of the error of the model
The `CV_err` fucntions
```{r}
CV_err(in_rasts = elev1, train = pts)
CV_err(in_rasts = c(elev1, elev2, elev3), train = pts)
CV_err(in_rasts = c(elev1, elev2, elev3), train = pts,
                    model_type = "glm")
```


# Run the model

```{r}
prob1 <- run_model(mod1, elev1)
prob2 <- run_model(mod2, c(elev1, elev2, elev3))
prob3 <- run_model(mod3, c(elev1, elev2, elev3), model_type = "glm")
prob4 <- run_model(mod4, c(elev1, elev2, elev3), model_type = "knn")
```

## Plot the results of the model

```{r}
plot(prob1["WET"], main = "Wetlands Probability (Simple)")
plot(prob2["WET"], main = "Wetlands Probability (Complex)")
plot(prob3, main = "Wetlands Probability (Logistic)")
plot(prob4["WET"],  main = "Wetlands Probability (knn)")
```


# Another option:

```{r}
plot(dem_to_prob(r, len = 36, train = pts))
```
